---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(badger)
library(usethis)

repo <- "centre-for-marine-applied-research/strings"
```

# strings

<!-- badges: start -->

[![License: GPL v3](https://img.shields.io/badge/License-GPLv3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0) `r badge_devel(repo, "blue")`

`r badge_codefactor(repo)`

`r badge_github_actions(repo)`

<!-- badges: end -->


The goal of strings is to help users compile, format, calculate, and visualize oceanographic data, as collected by the Centre for Marine Applied Research's (CMAR) Coastal Monitoring Program. The package can process temperature, dissolved oxygen, and salinity data measured by HOBO Pro V2, TidBiT, aquaMeasure DOT, aquaMeasure SAL, and/or VR2AR sensors.

## Installation

You can install the development version of strings from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Centre-for-Marine-Applied-Research/strings")
```

## Example 

Examples to come

```{r example}
library(strings)
## basic example code
```

